Precision line-by-line forward models for \'echelle spectra

### 2022-08-11 paper/paper1/ms.tex
add conclusions, almost there

Stellar abundance work involves precisely measuring line strengths (often reported as EWs) of different chemical constituents evinced in a star or substar's photosphere.  Relating those EWs back to physics can be done in a few ways.  Most easily, trends and patterns in the EWs can be assembled, and metal-rich and metal-poor clusters can be identified.  There exists a precision/accuracy tradeoff in the measurement process, usually stemming from the placement of the continuum, or assumptions about line blending.  Blas\'e offers an immediate solution to these challenges, since it starts from our best-guess for how nearby lines may be shaping the continuum.  Blas\'e appears to be a gateway to extremely fast and intervention-free way to obtain abundances, potentially useful for large surveys like APOGEE \citep{2017AJ....154...94M}, Gaia-ESO \citep{2012Msngr.147...25G}, RAVE \citep{2006AJ....132.1645S,}, and more.

This spirit resembles \texttt{ROBOSPECT} \citep{2013PASP..125.1164W}, and other approaches aimed at automatically measuring equivalent widths for a large number of stars.

One missing piece is either to post-process the blas\'e-output EW catalog with chemical labels (C, N, O, Si, Ba, Eu, etc.), or incorporate that information directly into the structure of blas\'e.  The latter case is intriguing.  For example, PHOENIX may not yet be aware of the existence of some obscure Lanthanum (La) line, possibly because the line was not yet understood and incorporated at the time of PHOENIX computation.  Rather than wait for PHOENIX to receive the necessary update, blas\'e could instantiate one or more such lines in the locations guided by the atomic line list.  This line could get initialized with some small amplitude, and would get added onto the underlying PHOENIX source as yet another freely tunable line.  In this way, all the other nearby lines would be used for assigning continuum and blending, but this free-standing Lanthanum line would acquire a value properly taking into account the impact of its neighbors.

@@

\section{Conclusions}
to-be-completed...

>>>>

Stellar abundance work involves precisely measuring line strengths (often reported as EWs) of different chemical constituents evinced in a star or substar's photosphere.  Relating those EWs back to physics can be done in a few ways.  Most easily, trends and patterns in the EWs can be assembled, and metal-rich and metal-poor clusters can be identified.  There exists a precision/accuracy tradeoff in the measurement process, usually stemming from the placement of the continuum, or assumptions about line blending.  Blas\'e offers an immediate solution to these challenges, since it starts from our best-guess for how nearby lines may be shaping the continuum.  Blas\'e appears to be a gateway to extremely fast and intervention-free way to obtain abundances, potentially useful for large surveys like APOGEE \citep{2017AJ....154...94M}, Gaia-ESO \citep{2012Msngr.147...25G}, RAVE \citep{2006AJ....132.1645S}, and more.

This spirit resembles \texttt{ROBOSPECT} \citep{2013PASP..125.1164W}, and other approaches aimed at automatically measuring equivalent widths for a large number of stars.  One missing piece here is either to post-process the blas\'e-output EW catalog with chemical labels (C, N, O, Si, Ba, Eu, etc.), or incorporate that information directly into the structure of blas\'e.  The latter case is intriguing.  For example, PHOENIX may not yet be aware of the existence of some obscure Lanthanum (La) line, possibly because the line was not yet understood and incorporated at the time of PHOENIX computation.  Rather than wait for PHOENIX to receive the necessary update, blas\'e could instantiate one or more such lines in the locations guided by the atomic line list.  This line could get initialized with some small amplitude, and would get added onto the underlying PHOENIX source as yet another freely tunable line.  In this way, all the other nearby lines would be used for assigning continuum and blending, but this free-standing Lanthanum line would acquire a value properly taking into account the impact of its neighbors.

@@

\section{Conclusions}
We have introduced an line-by-line approach to forward modelling stellar, substellar, and telluric spectroscopic data.  The approach relies on a key enabling technology, automatic differentiation, that enables nearly unlimited number of spectral lines to be fit simultaneously.  We initialize these lines to match precomputed synthetic stellar spectra, achieving excellent performance, and lending some confidence that the approach has a capacity to capture a tremendous amount of information at once.
